---
title       : "Workshop Prerequisites"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "August 25, 2016"
output      : slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

## Install a recent version of R

`SpaDES` requires R version `3.2.2` or greater.

Download and install the latest version of R from [https://cran.rstudio.com/](https://cran.rstudio.com/)

## Install the latest RStudio

Download and install RStudio from [https://www.rstudio.com/products/rstudio/download](https://www.rstudio.com/products/rstudio/download)

\* Preview versions are available from [https://www.rstudio.com/products/rstudio/download/preview/](https://www.rstudio.com/products/rstudio/download/preview/)

## Install `SpaDES`

Before we begin, we need to ensure we have installed the latest development version of the `SpaDES` package.

```{r install-SpaDES, eval=FALSE, echo=TRUE}
# install the SpaDES package from CRAN
install.packages("SpaDES")

# determine the SpaDES package version from CRAN
packageVersion("SpaDES")

# install the development version of SpaDES from GitHub
if (!require(devtools)) install.packages("devtools")
devtools::install_github("PredictiveEcology/SpaDES", ref = "development")
```

**NOTE:** If you don't have them installed already, installing `SpaDES` will install a number of additional spatial packages, some of which have additional system dependencies not covered by simply installing the R package.
See [this post](http://predictiveecology.org/2015/04/24/installing-R-spatial-packages.html) on how to ensure you can install the system dependencies required to install these packages.

## Create a new RStudio project

Lorem ipsum ...
