---
title       : "`SpaDES` in action"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "September 14, 2016"
output:
  ioslides_presentation:
    logo: images/predictive_ecology_logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

## Examples
 
- The [demo modules](https://github.com/PredictiveEcology/SpaDES/blob/master/inst/sampleModules/SpaDES_sampleModules/SpaDES_sampleModules.Rmd) in the `SpaDES` package
  
    - [caribouMovement](https://github.com/PredictiveEcology/SpaDES/blob/master/inst/sampleModules/caribouMovement/caribouMovement.R)  
    - [fireSpread](https://github.com/PredictiveEcology/SpaDES/blob/master/inst/sampleModules/fireSpread/fireSpread.R)  
    - [randomLandscapes](https://github.com/PredictiveEcology/SpaDES/blob/master/inst/sampleModules/randomLandscapes/randomLandscapes.R)  
            
- Land Cover Classification 2005 model ([LCC2005](http://htmlpreview.github.io/?https://github.com/PredictiveEcology/SpaDES-modules/blob/master/modules/LCC2005/LCC2005.html))

- Vegetation simulation (SpaDES-Landis)

- Agent based models – [wolf IBM](http://htmlpreview.github.io/?https://github.com/PredictiveEcology/SpaDES-modules/blob/master/modules/wolfAlps/wolfAlps.html)

- A shiny app on shinyapps.io (*e.g.*, [Proof of concept](https://spades.shinyapps.io/ForestChange_ProofOfConcept/))
   
## How `SpaDES` works

### Overview

Explain what DES is and how it works; why we want to use it.

## Modules

Lorem ipsum ...

## Events

Lorem ipsum ...

## Data objects

### Input objects

Lorem ipsum ...

### Output objects

Lorem ipsum ...

## Where to get help

- docs
- vignettes
- wiki
- user group
- bug reports

## Using pre-built modules

- demo modules included in the package
- `SpaDES` module repository (https://github.com/PredictiveEcology/SpaDES-modules)

```{r downloadModule-example, eval=FALSE, echo=TRUE}
downloadModule('wolfAlps')
```
