---
title       : "Building `SpaDES` modules"
author      : "Alex M Chubaty, Eliot McIntire"
date        : "September 14, 2016"
output      : slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

## New module template

Lorem ipsum ...

```{r new-module, echo=TRUE, eval=FALSE}
newModule('moduleName', file.path('path/to/my/module/directory'))
```

## Module metadata

Lorem ipsum ...

## New events

- explain how to use `scheduleEvent()`

- will the [`SpaDESaddin`](https://github.com/PredictiveEcology/SpaDES/issues/298) be ready?

## Working with data

- bundling data with your module

- external data sources

- checksums: need both windows and linux/Mac to verify file integrity

## Visualizations

- difference approaches during different stages of development etc.

    - include a figure shoiwng an idealized 'workflow of module/model development, testing, deployment, etc.'

- fast on-the-fly graphics useful for module debugging and development (*e.g.*, `Plot()`)

- file-based options for batch runs

- other "standard R" visualivations for publication etc.

## Summary statistics

- see [the wiki entry](https://github.com/PredictiveEcology/SpaDES/wiki/Summary-statistics-in-simulations)
