---
title       : "Simulation experiments and replication"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "August 25, 2016"
output:
  ioslides_presentation:
    logo: images/predictive_ecology_logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```


## Beyond `spades`

So far, we have run models with the `spades` function.  
`?spades` only has a few arguments:

    - debug
    - .plotInitialTime
    - .saveInitialTime
    - progress
    - cache
    
What if we want to do more stuff?

## Replication

What if we have a stochastic model and need many independent (monte carlo) runs?

The `experiment` function does this.

```{r experiment, eval=FALSE, echo=TRUE}
?experiment # for details
```

Generally, this creates problems because of the computational time required

## Replication 2

The `replicates` argument

It is as easy as `replicates = 2` to do 2 replicates.

```{r experiment2, eval=FALSE, echo=TRUE}
?experiment # for details

# See Example 5
#  ... run mySim from top of example
sims <- experiment(mySim, replicates = 2)
attr(sims, "experiment")$expDesign # shows 2 replicates of same experiment

```

## Scenario creation

- `experiment()`

## Parameter experiments

- `experiment()`

## Running parallel simulations
    
*e.g.*, on supercomputers/clusters

## Pattern Oriented Modeling

- use `POM()` for estimating unknown parameters
