---
title       : "Module integration"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "September 14, 2016"
output:
  ioslides_presentation:
    logo: images/predictive_ecology_logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

## Building models from modules

A model (as defined in the `SpaDES` world) consists of multiple interacting components (sub-models), which in the vocabulary of `SpaDES` we have been referring to as 'modules'

- One could imagine an example model:

    - caribou movement
    - vegetation dynamics
    - disturbance dynamics
    - data cleaning, downloading etc.
    
- And we would give this ensemble of modules a name, like "LCC2005" (or maybe even a better name, but we will go with this)

## LCC2005

([Return to LCC2005 model](http://htmlpreview.github.io/?https://github.com/PredictiveEcology/SpaDES-modules/blob/master/modules/LCC2005/LCC2005.html))

```{r exercise1}
# Run the first chunk to download the model to download to your computer. Then:
openModules("LCC2005", moduleDir)
```

- Examine this module
- What is different about it?

## Parent modules

- Currently, only used to identify a group of modules
- Uses "childModules" list entry
- Currently, a parent module can not have any events or functions **only metadata** and **only childModules** is used
- This may be changed in the future, but most likely by simplifying the number of entries in the metadata

<br>

- Will this decision (by SpaDEs developers) create problems?

<br>

- Can have grand-parents, great-grandparents, mixtures of parents, grand-parents etc.

## Parent modules - hypothetical example

The new **CFS-FD** model (Forest Dynamics Model)

- Has carbon, caribou, vegetation change, harvesting, climate, fire, insects
- But the vegetation module is actually a parent module with 3 modules:
    
    - mortality, growth, and regeneration modules
- fire module is actually 4 modules:
    
    - ignition, escape, spread, severity modules


## Parent modules -- where to put code?

- Likely you can imagine that there would be code you would want to put in the parent module
- We had many discussions about this
- We concluded: 

<div class="centered" style="color:#0000FF">*make a child module that does all the stuff you might think of as parent module content, add appropriate data dependencies (i.e., outputs are required by the other modules as inputs*</div>


## Child modules

- Everything that we have talked about to date is a child module
- This means that it is a stand alone module

## Using metadata

- There are 15 items in the metadata header
- The header is defined withe the `SpaDES` function `defineModule`
- Usually at the top of the module script, but it doesn't have to be
- In the future, this will likely expand, and gain functionality to allow increased automation

```{r define module}
# What are the 15 items?
```

- Explore different options

## Metadata

- Is there anything missing from the 15 items?


## Visual tools

There are a few tools that can help visualize the relationships between modules:

- `objectDiagram(sim)`
- `moduleDiagram(sim)`
- `eventDiagram(sim)`

What do/would these do?
Do they all work after `simInit`?



