---
title       : "Sharing modules and data"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "September 16, 2016"
output:
  ioslides_presentation:
    logo: images/predictive_ecology_logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
library(SpaDES)
```

## `SpaDES` module repositories

A 'module repository' is simply a web site that serves files using a particular directory structure (the same directory structure used in a local `SpaDES` module repo).

Our module repo is at https://github.com/PredictiveEcology/SpaDES-modules

This is the default repo in `SpaDES`

```{r module-repo-option, echo=TRUE, eval=TRUE}
getOption('spades.modulesRepo') ## default url prefix is GitHub
```

## What is GitHub?

[Github.com](https://github.com/) is a free\* code archive and hosting service.

Allows hosting of public and private code repositories, build around `git` version control software.

GitHub provides:

- code archiving/distribution
- version control
- publication (code, html pages, and others)
- collaboration
- bug tracker
- much much more...

## `shiny` apps

- simple apps: dashboards

- hosted apps at [shinyapps.io](http://www.shinyapps.io/) 

    - *e.g.*, [Proof of concept](https://spades.shinyapps.io/ForestChange_ProofOfConcept/)

## Data sources

- checksums
- externally hosted data
- include data with your module code
