---
title       : "Sharing modules and data"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "September 14, 2016"
output:
  ioslides_presentation:
    logo: images/predictive_ecology_logo.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

## `SpaDES` module repositories

- We have put together a GitHub repository that can hold `SpaDES` modules
**[github.com/PredictiveEcology/SpaDES-Modules](http://github.com/PredictiveEcology/SpaDES-Modules)**
- When put in this repository, it becomes

    - public  
    - easily downloadable with `downloadModule`
    
- So, at the start, most `SpaDES` modules will not be there
- e.g., SpaDES-LBM (SpaDES - Landis Biomass Succession) is not there yet (we would like to publish it first)

## Other `SpaDES` module repositories

- Of course, anybody can create their own repository as well (R has CRAN, Rforge, BioConductor and many lesser used ones)
- `downloadModule` has a `repo` argument

## GitHub

We, and many others, use GitHub extensively for all our group's work

- Like Dropbox, in the sense that there is a cloud version, and potentially many local copies all over the place
- Unlike Dropbox, the copies on people's computers are not automatically there
- Requires manual intervention

<br>

- Why use GitHub?

## Github for code

- Known as a "version control system" or VCS
- There have been many over the years, GitHub is "the best" currently
- inexpensive (free or cheap)

## GitHub Client

- For your local copy of the files, you need an extra piece of software on your computer (like the "Dropbox client")
- There are many

    - **[Gitkraken](http://gitkraken.com/)** is amazing and our group's prefered client

- Requires a bit of learning

    - [tutorial](https://guides.github.com/activities/hello-world/)

## `shiny` apps

- Massively powerful
- Allows the process of data wrangling, data visualization, data analysis, etc. to be made into interactive web (and mobile) apps
- By moving the web app development into R (instead of taking R outputs and putting them into a web development kit), means that the analysis power can be at the interactive stage
- Also, data analysts can be making web pages

## `shine` function

`SpaDES` has a simple function that takes any simList and makes a web app from it:

```{r shine}
?shine
```

<div class="centered">Try it!</div>

## Simple shiny apps

- hosted apps at [shinyapps.io](http://www.shinyapps.io/) 

    - *e.g.*, [Proof of concept](https://spades.shinyapps.io/ForestChange_ProofOfConcept/)

## Themes

- Lots of developers making shiny themes
- Often they are wrappers on javascript code
- So your look can be easily modified without many web development skills

## Shiny maps with leaflet

- [leaflet package](https://rstudio.github.io/leaflet/)

# Data sources

## Data sharing

- We have shown a way to specify default data sources

*Where was that?*

- We have shown a way to specify default data manipulations and data preprarations of those default data

*Where was that?*

## If there are complex data sets?

- And from many sources?
- Can still use `sourceURL` in `defineModule` and create an `.inputObjects` function which will do all the manipulations

## How to adequately describe data?

- It is clear that there is not enough information contained in the metadata to fully describe everything about the required dataset(s) type(s)
- **Use the .Rmd** file to describe more for human eyes
- It is very difficult to algorithmically define data in a generic way
- There are standards, but `SpaDES` doesn't tap into those (yet!)

## Overriding default datasets

- If a *user* passes an object that a module requires (in 'defineModule' metadata)
- The default data will not be used

- checksums
- externally hosted data
- include data with your module code
