---
title       : "Exercises: Building `SpaDES` modules"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "December 8, 2016"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, eval = FALSE)
```

# Scheduling

```{r scheduleEvent}
# scheduling event at t + 1 in fire is different than t + 1 in caribou explain
```

# Debugging

Let's cause an error in an existing module:

1. make a copy of the `caribouMovement` module, called `caribouMovementError`

```r
## hint: find where the caribouMovement module is located using
system.file("sampleModules", package = "SpaDES")
```

2. edit line XX to read:

```r
XXX
```

3. run the module normally and confirm that you get an error

4. how would you start debugging the error?

# Create a new module

Create a simple module that does one of the following:

1. generates a random map (hint: see `?gaussMap`) and updates the values in the raster cells;
2. model population dynamics as subpopulations within each raster cell.
