---
title       : "Exercises: Simulation Experiments and Replication"
author      : "Alex M Chubaty & Eliot McIntire"
date        : "December 8, 2016"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, eval = FALSE)
```

# `experiment` function

Often we want to run a simulation with a variety of parameter values as inputs. This is sometimes called a simulation experiment. The `experiment` function gives us an easy interface to this.

We will use the `establishment` module that we created in exercise 4a.

## download a module




```{r experiment}
library(SpaDES)
modulePath <- file.path(dirname(tempdir()), "modules")
downloadModule("establishment", path = modulePath)
setPaths(modulePath=modulePath)
library(ggplot2)

modules <- list("establishment")

mySim <- simInit(modules = modules)

# make sure the plotting device is clear
clearPlot()
spades(mySim)

```

## Create an experiment

1. Find out which parameters are in this module. (hint: where is the module? Can you open it easily from R?)
2. Pick one of the parameters and create a range of values for it
3. Following the structure indicated in example 4 of ?experiment, use `experiment` to run a `spades` call for each parameter set (note that `experiment` is just a wrapper around `spades`)
4. Inspect the experiment structure using `attributes(mySim)`
5. Create a plot showing on the x axis your parameter values, and on the y-axis something like `sum(mySim$establish[])`, i.e., the number of pixels that had an establishment event

## Advanced - Create a 2-parameter experiment

1. Repeat as above, but vary 2 parameters.

[See a solution here](http://htmlpreview.github.io/?https://github.com/PredictiveEcology/SpaDES-modules/blob/master/modules/establishment/establishment.html)
